---
title: 'Hippocampal dependence of value-based decisions: Statistical Analyses'
output:
github_document:
toc: yes
toc_float: yes
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(rmarkdown)
library(stringr)
library(plotly)
library(xlsx)
library(Hmisc)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('Transitivity_OpenAnalyses.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/CDSPart1/TransitivityOpen/', html_notebook(toc = T, toc_float = T, code_folding = 'hide'))}
options(scipen = 1, digits = 4)
```

Load workspace

```{r}
load("/Users/zeynepenkavi/Dropbox/CDSPart1/TransitivityOpen/Transitivity_OpenDataOrganizationWS052817.RData")
```

Group differences in intransitivies
--------------------------------------------------------

### Summary Statistics

```{r}
both.Intransitive %>%
  group_by(Task, Group) %>%
  summarise(mean_CleanIntr = mean(CleanIntr),
            median_CleanIntr = median(CleanIntr),
            sd_CleanIntr = sd(CleanIntr),
            mean_CleanPercentIntr = mean(CleanPercentIntr),
            median_CleanPercentIntr = median(CleanPercentIntr),
            sd_CleanPercentIntr = sd(CleanPercentIntr))
```

```{r}
both.Intransitive %>% 
  group_by(Task, Group) %>% 
  summarise(MeanCleanPercentIntr = mean(CleanPercentIntr, na.rm=T),
            SeCleanPercentIntr = sem(CleanPercentIntr),
            eb.low = MeanCleanPercentIntr - SeCleanPercentIntr,
            eb.high = MeanCleanPercentIntr + SeCleanPercentIntr) %>%
ggplot(aes(x = Group, y=MeanCleanPercentIntr, group = Task))+
  geom_point(aes(shape = Task))+
  geom_line(aes(linetype = Task))+
  geom_errorbar(aes(ymax = eb.high, ymin=eb.low), width=0.25)+
  ylab("Mean Percentage of Intransitivities")+
  xlab("")+
  theme_bw()+
  theme(axis.title.y = element_text(face="bold", size = 14),
        axis.text.x  = element_text(face="bold", size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))+
  scale_shape_discrete(breaks = c("choice", "numbers"),
                       labels = c("Value-based", "Numbers"))+
  scale_linetype_discrete(breaks = c("choice", "numbers"),
                          labels = c("Value-based", "Numbers"))
```


```{r warning=FALSE, message=FALSE}
ggsave("/Users/zeynepenkavi/Dropbox/CDSPart1/TransitivityOpen/CleanFigure2.png", width=6, height=4, dpi=300)
```

Looking at the plot we are interested in whether the difference between the two lines is the same for all groups. In other words: Is there a significant intereaction between task and group, i.e. is the effect of changing the task same for the MTL group as it is for the control groups.

To choose the correct model that would check for statistical differences between the groups we checked the assumptions for each possibility. Though all methods yield essentially the same answer we chose to use a linear mixed model with orthogonal contrasts because it was the most appropriate method. 

The first thing we could do would be a one-way ANOVA for both tasks checking whether the main dependent measure (percentage of intransitivities) differs depending on the group and task. The distribution of effect sizes within tasks, however, is not normal for either task, which is why this would not be an appropriate test. 

```{r message=FALSE} 
both.Intransitive %>%
  ggplot(aes(CleanPercentIntr, fill=Group))+
  geom_histogram(position="identity", alpha=0.5)+
  theme_bw()+
  xlab("Percentage of intransitivity")+
  facet_wrap(~Task)
```  


```{r}
shapiro.test(both.Intransitive[both.Intransitive$Task == "numbers",]$CleanPercentIntr)
```

```{r}
shapiro.test(both.Intransitive[both.Intransitive$Task == "choice",]$CleanPercentIntr)
```

To solve this we could try a non-parametric test (e.g. Kruskall-Wallis) but this wouldn't allow us to check the interaction of group by task and more importantly the variance in the effect size distributions are unequal. That is, as the Bartlett test below and the plot above shows variance in effect size is not independent of task.

```{r message=FALSE}
bartlett.test(CleanPercentIntr ~ Task, data = both.Intransitive)
```

To deal with this issue of task dependence of the variance we log transform the effect sizes.

```{r}
bartlett.test(log(CleanPercentIntr + 1) ~ Task, data = both.Intransitive)
```

Using transformed dependent variables we first confirm that the interactive model is the best fitting model by comparing it to nested simpler models.

```{r}
gm1a <- lm(log(CleanPercentIntr+1) ~ Task, both.Intransitive)#; summary(gm1a)
gm1b <- lm(log(CleanPercentIntr+1) ~ Group, both.Intransitive)# ; summary(gm1b)
gm2 <- lm(log(CleanPercentIntr+1) ~ Group+Task, both.Intransitive)# ; summary(gm2)
gm3 <- lm(log(CleanPercentIntr+1) ~ Group*Task, both.Intransitive)# ; summary(gm3)
```

```{r}
anova(gm1a, gm2, gm3)
```

```{r}
anova(gm1b, gm2, gm3)
```

```{r echo=FALSE}
rm(gm1a, gm1b, gm2)
```

So what does this interactive model say? To get a better understanding of this we first look at the contrasts used in this model.

```{r}
contrasts(both.Intransitive$Task)
```

```{r}
contrasts(both.Intransitive$Group)
```

Based on these contrasts the group differences in this model compare both patient groups to the healthy control alone. Accordingly the parameters of the linear model would have the following interpretations.

```{r}
summary(gm3)
```

b0 = mean percentage of intransitivity for both tasks for the C group is >0 (not interesting)
b1 = ETL group doesn't make significantly more intrans in CHOICE task! (good) - simple effect
b2 = MTL group DOES make sig more intrans in CHOICE task! (good) - simple effect
b3 = C group makes sig less intrans in NUMBERS task! (not surprising, easy task)
b4 = Is the effect of task in ETL group same as C. Yes.
b5 = Is the effect of task in MTL group same as C. Marginally no. 

As mentioned above, however, these are not orthogonal contrasts and are comparing both groups to Healthy controls only! But we are interested in comparing the MTL group to both control groups. To answer this question and to avoid overlapping variance we orthogonalize the contrasts. This would results in first comparing the ETL group to the C group and then the MTL group to BOTH CONTROL GROUPS!

```{r}
#Change the contrasts, make them orthogonal
both.Intransitive.contrast <- both.Intransitive
contrasts(both.Intransitive.contrast$Group) <- cbind(c(-1,1, 0), c(-1, -1, 2))
contrasts(both.Intransitive.contrast$Task) <- c(-1, 1)

gm3.con <- lm(log(CleanPercentIntr+1) ~ Group*Task, both.Intransitive.contrast) 
summary(gm3.con)
```

What does the model say now:

b0 = Unweighted grand mean (mean of group means) (sum(aggregate(CleanPercentIntr ~ Group, both.Intransitive.contrast, mean)[,2])/3)
b1 = Total group effect for ETL compared to healthy controls only (quantified)
b2 = Total group effect for MTL compared to both control groups (quantified)
b3 = Total task effect
b4 = Is the effect of task change same for ETL and C groups? (yes.)
b5 = Is the effect of task change same for MTL vs both control groups? (No!)

Since there are two measures per subject we check if a mixed model necessary comparing the log-likelihoods of a model with random effects to one without them. We find that that a model with random effects is indeed significantly better fit to data.

```{r}
gm3.lmer.con <- lmerTest::lmer(log(CleanPercentIntr+1) ~ Group*Task + (1|f.id), both.Intransitive.contrast, REML = F)

x2 = -2*logLik(gm3.con) +2*logLik(gm3.lmer.con)
x2
pchisq(x2, df=1, lower.tail=F)
```


```{r}
summary(gm3.lmer.con) 
```

The linear mixed model with orthogonal contrasts is the most appropriate analysis and reveals a significant group task interaction in the percentage of intransitivities. Accordingly the MTL group had a higher percentage of intransitivities in the choice task than the numbers task compared to both control groups, while the difference between the percentage of intransitivities did not differ between tasks between the health controls and the ETL group.

Lesion size and intransitivies
--------------------------------------------------------

```{r}
symmetry.data <- read.xlsx("/Users/zeynepenkavi/Dropbox/CDSPart1/Transitivity/TransitivityData/Symmetry_index_zeynep.xlsx", 1)

symmetry.data = both.Intransitive %>%
  filter(Task == 'choice') %>%
  mutate(ID = as.numeric(as.character(f.id))) %>%
  right_join(symmetry.data, by= 'ID') %>%
  drop_na()
```

Spearman correlation between instransitivity percentage and lesion size

```{r}
cor(symmetry.data$Symmetry.index, symmetry.data$CleanPercentIntr, method = "spearman")
```

Significance test for the Spearman correlation

```{r}
spearman.test(symmetry.data$Symmetry.index, symmetry.data$CleanPercentIntr)
```

Plot of correlation between 

```{r}
ggplot(symmetry.data, aes(Symmetry.index, CleanPercentIntr))+
  geom_point()+
  geom_smooth(method = 'loess', span = 2, color = "black", alpha = 0.1, linetype = "dashed")+
  theme_bw()+
  ylab("Percentage of Intransitve Choice")+
  xlab("Compromised Hippocampal Ratio")+
  theme(axis.title.y = element_text(face="bold", size = 14),
        axis.title.x  = element_text(face="bold", size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```


```{r}
ggsave("/Users/zeynepenkavi/Dropbox/CDSPart1/TransitivityOpen/CleanFigure3.png", width=4, height=4, dpi=300)

```

Simulations
------------------------------------------------------

```{r}
path = '/Users/zeynepenkavi/Dropbox/CDSPart1/TransitivityOpen/sim_output/'

fileList = list.files(path,pattern = "*_hardmax.csv")

read_csv_fn <- function(filename){
    ret <- read.csv(filename)
    ret$Source <- filename 
    ret
}

lapply(paste0(path, fileList), read_csv_fn)  %>% 
  bind_rows() %>%
  separate(Source, c("a", "b", "c", "d", "e", "f","g", "sim"),sep = "/") %>%
  select(pct_Intrans, sim) %>%
  separate(sim, c("a", "b", "c", "d", "noise", "e", "f"), sep = "_") %>%
  select(pct_Intrans, noise) %>%
  filter(noise %in% c(0.05, 0.25) == FALSE) %>%
  group_by(noise) %>%
  summarise(mean_Intrans = mean(pct_Intrans),
            sem_Intrans = sem(pct_Intrans)) %>%
  ggplot(aes(noise, mean_Intrans))+
  geom_point()+
  theme_bw()+
  geom_errorbar(aes(ymin = mean_Intrans-sem_Intrans, ymax = mean_Intrans+sem_Intrans), width=0.25)+
  ylab("Percentage of Intransivity")+
  xlab("Noise level")#+
  # ggtitle("Results of simulation using hardmax")
```

```{r}
fileList = list.files(path,pattern = "*_rbinom.csv")

lapply(paste0(path, fileList), read_csv_fn)  %>% 
  bind_rows() %>%
  separate(Source, c("a", "b", "c", "d", "e", "f","g", "sim"),sep = "/") %>%
  select(pct_Intrans, sim) %>%
  separate(sim, c("a", "b", "c", "d", "noise", "e", "f"), sep = "_") %>%
  select(pct_Intrans, noise) %>%
  filter(noise %in% c(0.05, 0.25) == FALSE) %>%
  group_by(noise) %>%
  summarise(mean_Intrans = mean(pct_Intrans),
            sem_Intrans = sem(pct_Intrans)) %>%
  ggplot(aes(noise, mean_Intrans))+
  geom_point()+
  theme_bw()+
  geom_errorbar(aes(ymin = mean_Intrans-sem_Intrans, ymax = mean_Intrans+sem_Intrans), width=0.25)+
  ylab("Percentage of Intransivity")+
  xlab("Noise level")+
  scale_y_continuous(breaks=seq(0,25,5), limits=c(0, 26))+
  ggtitle("Results of simulation flipping coin with noisy choice p")
```

```{r}
fileList = list.files(path,pattern = "*_epsilon.csv")

lapply(paste0(path, fileList), read_csv_fn)  %>% 
  bind_rows() %>%
  separate(Source, c("a", "b", "c", "d", "e", "f","g", "sim"),sep = "/") %>%
  select(pct_Intrans, sim) %>%
  separate(sim, c("a", "b", "c", "d", "noise", "e", "f"), sep = "_") %>%
  select(pct_Intrans, noise) %>%
  filter(noise %in% c(0.05, 0.25) == FALSE) %>%
  group_by(noise) %>%
  summarise(mean_Intrans = mean(pct_Intrans),
            sem_Intrans = sem(pct_Intrans)) %>%
  ggplot(aes(noise, mean_Intrans))+
  geom_point()+
  theme_bw()+
  geom_errorbar(aes(ymin = mean_Intrans-sem_Intrans, ymax = mean_Intrans+sem_Intrans), width=0.25)+
  ylab("Percentage of Intransivity")+
  xlab("Noise level")+
  scale_y_continuous(breaks=seq(0,25,5), limits=c(0, 26))+
  ggtitle("Results of simulation with epsilon greedy")
```

Alternative explanations of intransitivity
------------------------------------------------------

One alternative explanation of the higher level of intransitivities in the MTL group is about episodic memory deficits. Accordingly, the MTL group might be showing higher rates of intransitivity because they are unable to recall choices they have made earlier in the task. This hypothesis would predict a pattern of proportion of intransitive triplets each trial was involved in that increases towards the end of the task (the later the trial the more intransitive triplets it was involved in). The figure below shows the empirical change of intransitive triplet involvement with trial number.

```{r warning=FALSE, message=FALSE}
choice2.trial.data$Task <- "choice"
numbers.trial.data$Task <- "numbers"

both.trial.data <- rbind(choice2.trial.data[,c("f.id", "Group", "RT", "Task", "Trialnumber", "IntransTripleCounted")], numbers.trial.data[,c("f.id", "Group", "RT", "Task", "Trialnumber", "IntransTripleCounted")])

both.trial.data = both.Intransitive %>%
  select(f.id, CleanIntr, Task) %>%
  right_join(both.trial.data, by=c("f.id", "Task")) %>%
  mutate(PropInIntransTriplet = IntransTripleCounted/(CleanIntr*3)*100,
         Task = factor(Task, levels = c("choice", "numbers"), labels = c("Value-based", "Perceptual")))%>%
  filter(RT>0, RT<6000)
```

Note that most of the trials are not involved in any intransitivities so the averaged proportion of intransitivities for each trial number is pretty small (i.e why the y-axis is so small). 

```{r warning=FALSE, message = FALSE}
both.trial.data %>%
  ggplot(aes(x = Trialnumber, y = PropInIntransTriplet, group = Group, color = Group))+
  geom_smooth(method = "loess", span=5) +
  theme_bw()+
  facet_grid(~Task)+
  ylab("Percent of intransitive Triplets involved") +
  xlab("Order choice was made")
```

To test if there are any statistical differences both between the groups and throughout each task and between the two tasks we first compare three models where the proportion of intransitive triplets a trial is involved is regressed over the trial number and experimental group. The first model is additive, the second interactive and the third includes a quadratic effect of trial number as well. Model comparison shows that the addition of the interaction terms and the quadratic effect do not lead to significant improvements in fit. Thus we report the effects in the simplest additive model.

```{r warning=FALSE, message=FALSE}
mem1 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(Trialnumber)+Group*Task, both.trial.data)

#adding interaction of linear effect of RT between tasks and groups
mem2 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(Trialnumber)*Group*Task, both.trial.data)

#adding the quadratic effect
mem3 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(poly(Trialnumber,2))*Task*Group, both.trial.data)

anova(mem1, mem2, mem3)
```

```{r echo=FALSE}
rm(mem2, mem3)
```

The additive model suggests that contrary to the prediction of an episodic memory during the task account there is both no change in the proportion of intransitive triplets a trial in involved in throughout the task and this is true for all groups in both tasks.

```{r}
summary(mem1)
```

Response Times
------------------------------------------------------

### Intransitivities and response times (speed-accuracy tradeoff)

The y-axis is the proportion of intransitive triplets a trial is involved in. The higher lines for the numbers task might be confusing at first look given the few number of intransitivities in this task. It is because there are so few intransitivities that if a trial is involved in even a single intransitivity it translates to a larger proportions. The lower number if intransitivities for the numbers task is captured by the large error bars around the task (i.e. for each response time there are fewer non-zero data points involved in intransitivities compared to the choice task).

```{r message = FALSE, warning=FALSE}
both.trial.data %>%
  ggplot(aes(RT, PropInIntransTriplet, group=Group, color=Group))+
  # You don't want to plot the raw measure because then a single subject who has done a lot of intransitivities and is in general faster can make it seem like faster trials are associated with more intransitivities. You want the proportional involvement given the total number of intransitivities a subject makes over response time
  # ggplot(aes(RT, IntransTripleCounted, group=Group, color=Group))+
  theme_bw()+
  geom_smooth(method = "loess", span = 5)+
  facet_grid(~Task)+
  ylim(c(0,NA))+
  xlab("Response Time")+
  ylab("Percent of intransitive Triplets involved")
```

Is there a statistical difference in the effect of response times on intransitivities between the two tasks?  

We're not necessarily interested in whether the exact slopes are different in the two tasks. We can see they might be visually. The main question of interest is two-fold:  

- Is there a speed-accuracy tradeoff? Are shorter RTs associated with more intransitivities (in a linear model: does the linear effect of RT have a negative slope)  

- Does this differ between groups and across the two different tasks.  

First we do a model comparison and check whether the three-way interactions of RTs with groups and tasks as well as a quadratic effect of RTs lead to significant imporevements. Both do.   

```{r message=FALSE, warning=FALSE}
rt1 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(RT)+Group*Task, both.trial.data)

#adding interaction of linear effect of RT between tasks and groups
rt2 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(RT)*Group*Task, both.trial.data)

#adding the quadratic effect
rt3 = lmer(PropInIntransTriplet ~ (1|f.id)+scale(poly(RT,2))*Task*Group, both.trial.data)

anova(rt1, rt2, rt3)
```

```{r echo=FALSE}
rm(rt1, rt2)
```

So what does this model say? There is a significant linear effect of time where longer RTs are associated with more intransitivies (the opposite of a speed-accuracy tradeoff). There is a main effect of task where the numbers task has larger proportions of intransitivities but this as mentioned above is due to the lower number intransitivities per subject. The linear and quadratic effects of time are different for the ETL group compared to the control group. The increase in the proportion of intransitivities for the MTL group is less than the increase in this proportion for the control group (this isn't interesting because the control group makes barely any intransitivities in the perceptual task). The change in the linear effect of time in the numbers task compared to the choice task is less this change for the control group (also not interesting because there is a quadratic effect of time for the ETL group and this change is not significant).  

As qualitatively suggested in the above figure there is no negative slopes indicating a speed accuracy tradeoff for either task. Also crucially the interactions for the significant effects of time for each group are not significant: The interaction between the linear effect time and task for the control group, the threeway interaction between the linear effect of time and task for the MTL group and the threeway interaction between the quadratic effect of time and task for the ETL group are not significant. That is, the effect of time on intransitivities is the same for both tasks.  

```{r warning=FALSE, message = FALSE}
summary(rt3)
```

### Response times for groups

```{r}
ggplot(data = both.trial.data, aes(x = Trialnumber, y = RT, group = Group, linetype = Group))+
  geom_smooth(method = "lm", color = "black")+
  theme_bw()+
  facet_grid(~Task)+
  xlab("Trial number")+
  ylab("Response time")
```

```{r}
both.trial.data %>%
  group_by(Group, Task) %>%
  summarise(mean_RT = mean(RT),
            sd_RT = sd(RT),
            median_RT = median(RT))
```

Full model for above graph. Not run because too long.

```{r eval=FALSE}
rt.lmer1 <- lmerTest::lmer(scale(RT) ~ Group*Task*scale(Trialnumber) + (1|f.id), data = RT.df[RT.df$RT>0,])

summary(rt.lmer1)
```

Group differences response times (reported)

```{r}
summary(lmerTest::lmer(scale(RT) ~ Group + (1|f.id), data = choice2.trial.data[choice2.trial.data$RT>0,]))
```

Idiosyncratic stimulus effects
------------------------------------------------------

```{r}
id.df = choice2.trial.data %>%
  select(IntransTripleCounted, Image_right, Image_left, f.id) %>%
  gather(key, value, -IntransTripleCounted, -f.id) %>%
  group_by(f.id,value) %>%
  summarise(sum_Intrans = sum(IntransTripleCounted))

summary(aov(sum_Intrans ~ factor(value) + Error(f.id/value), data = id.df))
#For exact values
# str(summary(aov(sum_Intrans ~ factor(value) + Error(f.id/value), data = id.df)))
```

```{r echo=FALSE}
rm(id.df)
```

Remaining comments:
Elke (l 233): This can only be the case for the final third triplet, no? how would the initial two pairwise choice have been made without value construction???

Plot of the average number of intransitivities for each trial number that was the third/last seen pair in an intransitive triplet.

```{r}
both.triplet.data %>%
  group_by(Task, ThirdTrial, Group) %>%
  mutate(CleanIntr = ifelse(Intrans == 1 & Error == 0,1, 0)) %>%
  summarise(mean_Intr = mean(CleanIntr, na.rm=T)) %>%
  drop_na() %>%
  arrange(Task, mean_Intr)%>%
  ggplot(aes(ThirdTrial, mean_Intr, group=Group, color=Group))+
  theme_bw()+
  geom_smooth(method = "lm")+
  # geom_smooth(method = "loess", span = 5)+
  facet_grid(~Task)+
  ylab("Average number of intransitives")+
  xlab("Trial number (when third pair in intransitive triplet)")
```

```{r}
both.triplet.data = both.triplet.data %>%
  mutate(CleanIntr = ifelse(Intrans == 1 & Error == 0,1, 0))

summary(lmer(CleanIntr ~ (1|f.id)+Task*Group*ThirdTrial, both.triplet.data))
```

```{r}
both.triplet.data %>%
  group_by(f.id, ThirdTrial, Group, Task) %>%
  summarise(PIntransWhenLast= sum(CleanIntr)/n()) %>%
  ggplot(aes(ThirdTrial, PIntransWhenLast, group=Group, color=Group))+
  # geom_smooth(method='loess', span=5)+
  geom_smooth(method='lm')+
  facet_grid(~Task)+
  theme_bw()
  
```

```{r}
tmp = both.triplet.data %>%
  group_by(f.id, ThirdTrial, Group, Task) %>%
  summarise(PIntransWhenLast= sum(CleanIntr)/n())

summary(lmer(PIntransWhenLast ~ (1|f.id)+Task*Group*ThirdTrial,tmp))
```

```{r}
both.triplet.data %>%
  group_by(f.id, ThirdTrial, Group, Task) %>%
  summarise(NumTimesLast = n(),
            IntransWhenLast = sum(CleanIntr),
            PIntransWhenLast= sum(CleanIntr)/n()) %>%
  arrange(Task)
```

Speed accuracy tradeoff on triplet level:

```{r}
both.triplet.data = both.triplet.data %>%
  mutate(Task = factor(Task, levels = c("choice", "numbers"), labels = c("Value-based", "Perceptual"))) %>%
  left_join(both.trial.data[,c("Task", "f.id", "Trialnumber", "RT")], by = c("Task", "f.id", "TrialA" = "Trialnumber")) %>%
  rename(RT_A = RT) %>%
    left_join(both.trial.data[,c("Task", "f.id", "Trialnumber", "RT")], by = c("Task", "f.id", "TrialB" = "Trialnumber")) %>%
  rename(RT_B = RT) %>%
    left_join(both.trial.data[,c("Task", "f.id", "Trialnumber", "RT")], by = c("Task", "f.id", "TrialC" = "Trialnumber")) %>%
  rename(RT_C = RT) %>%
  drop_na()
```

```{r}
both.triplet.data %>%
  select(RT_A, RT_B, RT_C, Task, CleanIntr, Group, f.id) %>%
  gather(key, value, -Task, -CleanIntr, -f.id, -Group) %>%
  ggplot(aes(value, CleanIntr, group=Group, color=Group))+
  geom_smooth(method='glm')+
  theme_bw()+
  facet_grid(key~Task)+
  xlab("Response time")+
  ylab("Intransitive triplet")
```

In the linear regression I chose to look only at the effect of the response time in the third trial because:  
- that's the trial that would determine whether a trial is intransitive or not 
- the graph suggests that the relationship between response times and intransitive triplets is the same for the three trials
- the response times for each trial in a triplet are higly correlated with each other
- Note: the full interactive model with all three response times does lead to significantly improved model but becomes too uninterpretable

```{r eval=FALSE}
sa1 = lmer(CleanIntr ~ (1|f.id)+Task*Group+scale(RT_C), both.triplet.data)
sa2 = lmer(CleanIntr ~ (1|f.id)+Task*Group*scale(RT_C), both.triplet.data)
sa3 = lmer(CleanIntr ~ (1|f.id)+Task*Group+scale(RT_A)+scale(RT_B)+scale(RT_C), both.triplet.data)
sa4 = lmer(CleanIntr ~ (1|f.id)+Task*Group*scale(RT_C)+scale(RT_B)+scale(RT_A), both.triplet.data)
sa5 = lmer(CleanIntr ~ (1|f.id)+Task*Group+scale(RT_C)*scale(RT_B)*scale(RT_A), both.triplet.data)
sa6 = lmer(CleanIntr ~ (1|f.id)+Task*Group*scale(RT_C)*scale(RT_B)*scale(RT_A), both.triplet.data)

#need the interaction of rt_c
anova(sa1, sa2)
#additive with 3 rt's is better than only the third rt
anova(sa1, sa3)
#interactive with 3'rts is better than additive with 3 rt's
anova(sa3, sa4)
#for interactive do you need the main of the other two  - yes
anova(sa2, sa4)
#when using all three rt's is making them interactive better? - yes
anova(sa3, sa5)
#is the full interactive model with 3 rt's better than adding the other two rt's additively?-yes
anova(sa4, sa6)
#is the full interactive model with 3 rt's better than adding the rt interactions additively?-yes
anova(sa5, sa6)
```

The model confirms that

```{r}
summary(glmer(CleanIntr ~ (1|f.id)+Task*Group*scale(RT_C), family = binomial(link = "logit"), both.triplet.data))
```

Correlations between response times for each trial in a triplet

```{r}
both.triplet.data %>%
  select(Task, RT_A, RT_B, RT_C, Group, f.id) %>%
  gather(key, value, -Task, -RT_C, -Group, -f.id) %>%
  ggplot(aes(RT_C, value, group=Group, color=Group))+
  geom_smooth(method="lm")+
  theme_bw()+
  facet_grid(key ~ Task)+
  xlab("Response time for the third trial in the triplet")+
  ylab("Response times for the first \n and second trials in triplet")
```
